---
title: "What is data scientist - HW1"
author: "Jiayin Liu"
format: html
editor: visual
---

# Homework 1
## Part 1 -- Answer the question
### What do you think being a data scientist is about?
I think being a data scientist is about using data to answer meaningful questions and support other department for decision-making.
Based on the class material and the working experience, I think the following parts is really critical for being a data scientist:
- The research question should be clear.
- Data cleaning and management should be careful.
- Method of analysis should be chosen after detailed consideration.
- Interpreting the result in proper language.
- The result should be communicated to others clearly and accurately.

### What differences/similarities do you see between data scientists and statisticians?
I think data scientists and statisticians have many similarities. They both work with data, and quantitative methods are used. They both target on getting a proper, accurate conclusion on the research question. 
For the difference, I think statisticians focus more on the model, inference, and study design, but data scientists focus more on programming and data management. 

### How do you view yourself in relation to these two areas?
I think I'm some position between data scientist and statisticians. As a data analyst in maternal and child health research, I work on proposal analysis, but I also responsible for the data management and data harmonization at work.

## Part 2 -- Include R code

```{r}
y <- density(iris$Petal.Width) 
```

### class of object y
```{r,echo=FALSE}
class(y)
```
### type of object y
```{r,echo=FALSE}
typeof(y)
```
### structure of object y
```{r,echo=FALSE}
str(y)
```

